Visualizing predictions

### 2021-02-09 effects_writeup.Rnw
Fiddling
Autocommit

#library(shellpipes)
#sourceFiles()

@

<<simple_sim, echo=FALSE>>=
set.seed(101)
N <- 100
x1_min <- 1
x1_max <- 9
b0 <- 0.3
b1 <- 0.1
b2 <- -0.6
x2_levels <- factor(c("A", "B"))
df <- expand.grid(x1u = runif(n=N, min=x1_min, max=x1_max)
	, x2u = x2_levels
)
X <- model.matrix(~x1u + x2u, df)
betas <- c(b0, b1, b2)
df$y <- rnorm(nrow(df), mean= X %*% betas, sd=1)
df2 <- df
df <- transform(df
	, x1c = drop(scale(x1u, scale=FALSE)) 
	, x1s = drop(scale(x1u, center=FALSE))
	, x1sd = drop(scale(x1u))
)
head(df)
@

@@

<<compare_baseR, echo=FALSE>>=
load("predict_plots.rda")
@

@@

\begin{figure}[H]
\begin{center}
<<compare_baseR_plot, fig=TRUE, echo=FALSE>>=
print(x1_plot)
@
\end{center}
\caption{Conditional predictions.}
\end{figure}

>>>>

load("predict_plots.rda")

## How to pass arguments??
#library(shellpipes)
#sourceFiles()

@
<<>>=

ls()

@
<<simple_sim, echo=FALSE>>=
set.seed(101)
N <- 100
x1_min <- 1
x1_max <- 9
b0 <- 0.3
b1 <- 0.1
b2 <- -0.6
x2_levels <- factor(c("A", "B"))
df <- expand.grid(x1u = runif(n=N, min=x1_min, max=x1_max)
	, x2u = x2_levels
)
X <- model.matrix(~x1u + x2u, df)
betas <- c(b0, b1, b2)
df$y <- rnorm(nrow(df), mean= X %*% betas, sd=1)
df2 <- df
df <- transform(df
	, x1c = drop(scale(x1u, scale=FALSE)) 
	, x1s = drop(scale(x1u, center=FALSE))
	, x1sd = drop(scale(x1u))
)
head(df)
@

@@

<<compare_baseR, echo=FALSE>>=
@

@@

\begin{figure}[H]
\begin{center}
<<compare_baseR_plot, fig=TRUE, echo=FALSE>>=
print(plot(1:10))
## print(x1_plot)
@
\end{center}
\caption{Conditional predictions.}
\end{figure}
